Comprehensive Comparison of Deep Learning Models for Lung and COVID-19 Lesion Segmentation in CT scans

### 2020-11-30 ms.tex
fix README.md
simplify Makefile

\begin{document}
\DTLloaddb{keys_values}{results/keys-values.csv}

@@

\begin{figure}[!t]
	\centering
	\begin{tikzpicture}[]
		\node[] (input) {\includegraphics[scale=0.3]{results/lesion-segmentation-a-image}};
		\node[draw] (architecture) [right=0.5cm of input, minimum height=2.8cm, minimum width=1.2cm]{\hspace{-2em}\rotatebox{90}{architecture}};
		\node[draw] (encoder) [right=1cm of input, minimum height=2cm]{\rotatebox{90}{encoder}};
		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{results/lesion-segmentation-a-prediction-train-masked-image}};
		\node[draw, below=0.5cm of output, circle] (loss){$\mathcal{L}$};
		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{results/lesion-segmentation-a-mask-train-masked-image}};
		\node[] at (0, 1){$\bm{X}$};
		\node[] at (5.2, 1){$\hat{\bm{Y}}$};
		\node[] at (5.2, -4){$\bm{Y}$};
		\draw[->] (input) -- node{} (architecture);
		\draw[->] (architecture) -- node{} (output);
		\draw[->] (output) -- node{} (loss);
		\draw[->] (mask) -- node{} (loss);
		\draw[->] (loss) -| node[shift={(0, -0.2)}]{backpropagation} (architecture);
	\end{tikzpicture}
	\caption{High level overview of a lesion segmentation model with an architecture consisting of an encoder trained using a single training augmented image.
	$\bm{X}$ is the input, $\bm{Y}$ is the target mask, $\hat{\bm{Y}}$ is the predicted mask and $\mathcal{L}$ is the loss function, which in this case is the Dice loss.
	Green and red pixels at $\hat{\bm{Y}}$ depict correctly and falsely classified pixels, while green pixels at $\bm{Y}$ depict the pixels of the target mask.
	Arrows denote the flow of the feed-forward and backpropagation pass.
	$\bm{X}$ is passed to the architecture consisting of a specific encoder and $\hat{\bm{Y}}$ is calculated.
	Then $\hat{\bm{Y}}$ and $\bm{Y}$ are used to calculate the loss, which is then used to backpropagate the error to the weights.
	This procedure is repeated for a number of times using more training examples till $\mathcal{L}$ converges.}
	\label{fig:highleveloverview}
\end{figure}

@@

\begin{figure*}[!t]
	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{results/lung-segmentation-hist}}
	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{results/lesion-segmentation-a-hist}}
	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{results/lesion-segmentation-b-hist}}
	\caption{Histogram plots of the normalized pixel intensities for the images (blue) and target masks (orange) for each experimental setup.
	The vertical axis depicts the normalized frequencies of each pixel intensity in the logarithmic scale.
	The outlier bar at zero is because most of the pixels in the target masks are near zero.}
	\label{fig:hist}
\end{figure*}

@@

\begin{figure}[!t]
	\centering
	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Unet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Linknet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-FPN-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-PSPNet-\best-masked-image}}
	\\
	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Unet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Linknet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-FPN-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-PSPNet-\best-masked-image}}
	\\
	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Unet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Linknet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-FPN-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-PSPNet-\best-masked-image}}
	\\
	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Unet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-Linknet-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-FPN-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lung-segmentation-PSPNet-\worst-masked-image}}
	\\
	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Unet-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-Linknet-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-FPN-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-a-PSPNet-\worst-masked-image}}
	\\
	\setcounter{subfigure}{0}
	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Unet-\worst-masked-image}}
	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-Linknet-\worst-masked-image}}
	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-FPN-\worst-masked-image}}
	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{results/lesion-segmentation-b-PSPNet-\worst-masked-image}}
	\caption{Predicted masks on a CT scan image from the test data for $24$ out of $600$ of the models.
	The three top columns correspond to predicted masks generated from a model with the best encoder and the bottom three for the worst.
	Rows correspond to each of the four architectures.
	Green and red depict correctly and falsely classified pixels respectively.}
	\label{fig:predictedmasks}
\end{figure}

\begin{figure}[!t]
	\centering
	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-scatter-dice-vs-num-parameters}}
	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
	\\
	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{results/diff-scatter-dice-vs-num-parameters}}
	\caption{Dice vs.\ number of parameters for the three experimental setups and the difference between lesion segmentation B and A.
	The green regions depict the kernel density estimate for all points using Gaussian kernels.
	The method used to calculate the estimator bandwidth was Scott and the points are assumed to be equally weighted.}
	\label{fig:dicevsnumparameters}
\end{figure}

\begin{table*}[!t]
	\centering
	\caption{Metrics}
	\label{table:metrics}
	\setlength\tabcolsep{6.5pt}
	\scalebox{0.35}{\input{results/metrics.tex}}
\end{table*}

@@

\begin{figure}[!t]
	\centering
	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-train-loss}}
	\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-validation-loss}}
	\\
	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-train-loss}}
	\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-validation-loss}}
	\\
	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-train-loss}}
	\subfloat{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-validation-loss}}
	\\
	\setcounter{subfigure}{0}
	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-train-diff-loss}}
	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-validation-diff-loss}}
	\caption{Training and validation loss plots with mean (line) and standard deviation (patch) for the four architectures segregated upon encoders for each experimental setup.
	Rows correspond to experimental setups and the difference between lesion segmentation B and A and columns correspond to train and validation losses.}
	\label{fig:loss}
\end{figure}

\begin{figure}[!t]
	\centering
	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-boxplot-dice}}
	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-a-boxplot-dice}}
	\\
	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{results/lesion-segmentation-b-boxplot-dice}}
	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{results/initialization-boxplot-dice}}
	\caption{Boxplots of Dice for the three experiments and for each architecture in (a), (b) and (c) and weight initialization for all experiments in (d).}
	\label{fig:box}
\end{figure}

@@

\begin{figure*}[!t]
	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-mask--volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-Unet-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-Linknet-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-FPN-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lung-segmentation-PSPNet-None-volume}}
	\\
	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-mask--volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-Unet-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-Linknet-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-FPN-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-a-PSPNet-None-volume}}
	\\
	\setcounter{subfigure}{0}
	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-mask--volume}}
	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-Unet-None-volume}}
	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-Linknet-None-volume}}
	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-FPN-None-volume}}
	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{results/lesion-segmentation-b-PSPNet-None-volume}}
	\caption{Reconstructed volumes from predicted masks.
	Reconstruction was done by stacking the predicted masks on the z-axis and then applying the marching cubes algorithm.}
	\label{fig:volumes}
\end{figure*}

@@

\begin{figure}[!t]
	\centering
	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-None-before-weights}}
	\subfloat{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-None-after-weights}}
	\\
	\setcounter{subfigure}{0}
	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-imagenet-before-weights}}
	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{results/lung-segmentation-Unet-imagenet-after-weights}}
	\caption{Grid visualization of the $64$ weights with size $7\times 7$ of the first convolutional layer for the Unet architecture with ResNet-18 encoder.
	The two left and two right grids correspond to random and ImageNet pretrained initialization, respectively.
	The data range of the colormap of the images has been adjusted in the range $[-0.4, 0.4]$.}
	\label{fig:weights}
\end{figure}

@@

\bibliographystyle{elsarticle-num}
\bibliography{ms}

>>>>

\begin{document}
\DTLloaddb{keys_values}{tmp/keys-values.csv}

@@

\begin{figure}[!t]
	\centering
	\begin{tikzpicture}[]
		\node[] (input) {\includegraphics[scale=0.3]{tmp/lesion-segmentation-a-image}};
		\node[draw] (architecture) [right=0.5cm of input, minimum height=2.8cm, minimum width=1.2cm]{\hspace{-2em}\rotatebox{90}{architecture}};
		\node[draw] (encoder) [right=1cm of input, minimum height=2cm]{\rotatebox{90}{encoder}};
		\node[] (output) [right=0.5cm of encoder]{\includegraphics[scale=0.3]{tmp/lesion-segmentation-a-prediction-train-masked-image}};
		\node[draw, below=0.5cm of output, circle] (loss){$\mathcal{L}$};
		\node[] (mask) [below=0.5cm of loss]{\includegraphics[scale=0.3]{tmp/lesion-segmentation-a-mask-train-masked-image}};
		\node[] at (0, 1){$\bm{X}$};
		\node[] at (5.2, 1){$\hat{\bm{Y}}$};
		\node[] at (5.2, -4){$\bm{Y}$};
		\draw[->] (input) -- node{} (architecture);
		\draw[->] (architecture) -- node{} (output);
		\draw[->] (output) -- node{} (loss);
		\draw[->] (mask) -- node{} (loss);
		\draw[->] (loss) -| node[shift={(0, -0.2)}]{backpropagation} (architecture);
	\end{tikzpicture}
	\caption{High level overview of a lesion segmentation model with an architecture consisting of an encoder trained using a single training augmented image.
	$\bm{X}$ is the input, $\bm{Y}$ is the target mask, $\hat{\bm{Y}}$ is the predicted mask and $\mathcal{L}$ is the loss function, which in this case is the Dice loss.
	Green and red pixels at $\hat{\bm{Y}}$ depict correctly and falsely classified pixels, while green pixels at $\bm{Y}$ depict the pixels of the target mask.
	Arrows denote the flow of the feed-forward and backpropagation pass.
	$\bm{X}$ is passed to the architecture consisting of a specific encoder and $\hat{\bm{Y}}$ is calculated.
	Then $\hat{\bm{Y}}$ and $\bm{Y}$ are used to calculate the loss, which is then used to backpropagate the error to the weights.
	This procedure is repeated for a number of times using more training examples till $\mathcal{L}$ converges.}
	\label{fig:highleveloverview}
\end{figure}

@@

\begin{figure*}[!t]
	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Normalized frequencies}\subfloat[Lung segmentation]{\includegraphics[width=0.33\textwidth]{tmp/lung-segmentation-hist}}
	\subfloat[Lesion segmentation A]{\includegraphics[width=0.33\textwidth]{tmp/lesion-segmentation-a-hist}}
	\subfloat[Lesion segmentation B]{\includegraphics[width=0.33\textwidth]{tmp/lesion-segmentation-b-hist}}
	\caption{Histogram plots of the normalized pixel intensities for the images (blue) and target masks (orange) for each experimental setup.
	The vertical axis depicts the normalized frequencies of each pixel intensity in the logarithmic scale.
	The outlier bar at zero is because most of the pixels in the target masks are near zero.}
	\label{fig:hist}
\end{figure*}

@@

\begin{figure}[!t]
	\centering
	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Unet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Linknet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-FPN-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-PSPNet-\best-masked-image}}
	\\
	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Unet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Linknet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-FPN-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-PSPNet-\best-masked-image}}
	\\
	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Unet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Linknet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-FPN-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-PSPNet-\best-masked-image}}
	\\
	\rotatebox[origin=l]{90}{\tiny Lung segmentation}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Unet-\best-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-Linknet-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-FPN-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lung-segmentation-PSPNet-\worst-masked-image}}
	\\
	\rotatebox[origin=l]{90}{\tiny Lesion segmentation A}\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Unet-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-Linknet-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-FPN-\worst-masked-image}}
	\subfloat{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-a-PSPNet-\worst-masked-image}}
	\\
	\setcounter{subfigure}{0}
	\rotatebox[origin=l]{90}{\tiny Lesion segmentation B}\subfloat[{\tiny Unet}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Unet-\worst-masked-image}}
	\subfloat[{\tiny Linknet}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-Linknet-\worst-masked-image}}
	\subfloat[{\tiny FPN}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-FPN-\worst-masked-image}}
	\subfloat[{\tiny PSPNet}]{\includegraphics[width=0.12\textwidth]{tmp/lesion-segmentation-b-PSPNet-\worst-masked-image}}
	\caption{Predicted masks on a CT scan image from the test data for $24$ out of $600$ of the models.
	The three top columns correspond to predicted masks generated from a model with the best encoder and the bottom three for the worst.
	Rows correspond to each of the four architectures.
	Green and red depict correctly and falsely classified pixels respectively.}
	\label{fig:predictedmasks}
\end{figure}

\begin{figure}[!t]
	\centering
	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-scatter-dice-vs-num-parameters}}
	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-scatter-dice-vs-num-parameters}}
	\\
	\rotatebox[origin=l]{90}{\hspace{2em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-scatter-dice-vs-num-parameters}}
	\subfloat[Lesion segmentation B-A]{\includegraphics[width=0.24\textwidth]{tmp/diff-scatter-dice-vs-num-parameters}}
	\caption{Dice vs.\ number of parameters for the three experimental setups and the difference between lesion segmentation B and A.
	The green regions depict the kernel density estimate for all points using Gaussian kernels.
	The method used to calculate the estimator bandwidth was Scott and the points are assumed to be equally weighted.}
	\label{fig:dicevsnumparameters}
\end{figure}

\begin{table*}[!t]
	\centering
	\caption{Metrics}
	\label{table:metrics}
	\setlength\tabcolsep{6.5pt}
	\scalebox{0.35}{\input{tmp/metrics.tex}}
\end{table*}

@@

\begin{figure}[!t]
	\centering
	\rotatebox[origin=l]{90}{\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-train-loss}}
	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-validation-loss}}
	\\
	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-train-loss}}
	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-validation-loss}}
	\\
	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-train-loss}}
	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-validation-loss}}
	\\
	\setcounter{subfigure}{0}
	\rotatebox[origin=l]{90}{\scriptsize Lesion segmentation B-A}\subfloat[Train loss]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-train-diff-loss}}
	\subfloat[Validation loss]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-validation-diff-loss}}
	\caption{Training and validation loss plots with mean (line) and standard deviation (patch) for the four architectures segregated upon encoders for each experimental setup.
	Rows correspond to experimental setups and the difference between lesion segmentation B and A and columns correspond to train and validation losses.}
	\label{fig:loss}
\end{figure}

\begin{figure}[!t]
	\centering
	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice(\%)}\subfloat[Lung segmentation]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-boxplot-dice}}
	\subfloat[Lesion segmentation A]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-a-boxplot-dice}}
	\\
	\rotatebox[origin=l]{90}{\hspace{1.5em}\scriptsize Dice(\%)}\subfloat[Lesion segmentation B]{\includegraphics[width=0.24\textwidth]{tmp/lesion-segmentation-b-boxplot-dice}}
	\subfloat[Initialization]{\includegraphics[width=0.24\textwidth]{tmp/initialization-boxplot-dice}}
	\caption{Boxplots of Dice for the three experiments and for each architecture in (a), (b) and (c) and weight initialization for all experiments in (d).}
	\label{fig:box}
\end{figure}

@@

\begin{figure*}[!t]
	\rotatebox[origin=l]{90}{\hspace{1em}\scriptsize Lung segmentation}\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-mask--volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-Unet-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-Linknet-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-FPN-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lung-segmentation-PSPNet-None-volume}}
	\\
	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation A}\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-mask--volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-Unet-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-Linknet-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-FPN-None-volume}}
	\subfloat{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-a-PSPNet-None-volume}}
	\\
	\setcounter{subfigure}{0}
	\rotatebox[origin=l]{90}{\hspace{0.8em}\scriptsize Lesion segmentation B}\subfloat[Mask]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-mask--volume}}
	\subfloat[Unet]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-Unet-None-volume}}
	\subfloat[Linknet]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-Linknet-None-volume}}
	\subfloat[FPN]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-FPN-None-volume}}
	\subfloat[PSPNet]{\includegraphics[width=0.20\textwidth]{tmp/lesion-segmentation-b-PSPNet-None-volume}}
	\caption{Reconstructed volumes from predicted masks.
	Reconstruction was done by stacking the predicted masks on the z-axis and then applying the marching cubes algorithm.}
	\label{fig:volumes}
\end{figure*}

@@

\begin{figure}[!t]
	\centering
	\rotatebox[origin=l]{90}{\scriptsize Random initialization}\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-None-before-weights}}
	\subfloat{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-None-after-weights}}
	\\
	\setcounter{subfigure}{0}
	\rotatebox[origin=l]{90}{\scriptsize ImageNet initialization}\subfloat[Before training]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-imagenet-before-weights}}
	\subfloat[After training]{\includegraphics[width=0.24\textwidth]{tmp/lung-segmentation-Unet-imagenet-after-weights}}
	\caption{Grid visualization of the $64$ weights with size $7\times 7$ of the first convolutional layer for the Unet architecture with ResNet-18 encoder.
	The two left and two right grids correspond to random and ImageNet pretrained initialization, respectively.
	The data range of the colormap of the images has been adjusted in the range $[-0.4, 0.4]$.}
	\label{fig:weights}
\end{figure}

@@

\bibliographystyle{elsarticle-num}
\bibliography{ms.bib}
